### 2016-03-21 manuscript.Rnw
acknowledge Scott & Ross for commenting pre-print

We would like to thank the organizers of the OpenTree of Life APIs hackathon
that was held at the University of Michigan, Ann Arbor, 15-19 September, 2014,
where the development of \texttt{rotl} was started. We would also like to thank
Scott Chamberlain (rOpenSci) for providing a thorough code review and Shinichi
Nakagawa and Alistair Senior for their help in developing the package's
meta-analysis vignette. DJW was supported by NIH Grant R01-GM101352. FM was
supported by iDigBio, and therefore this material is based upon work supported
by the National Science Foundation’s Advancing Digitization of Biodiversity
Collections Program (Cooperative Agreement EF-1115210).

>>>>

We would like to thank the organizers of the OpenTree of Life APIs hackathon
that was held at the University of Michigan, Ann Arbor, 15-19 September, 2014,
where the development of \texttt{rotl} was started. We would also like to thank
Scott Chamberlain (rOpenSci) for providing a thorough code review, Scott
Chamberlain and Ross Mounce for commenting on the pre-print version of this
manuscript, and Shinichi Nakagawa and Alistair Senior for their help in
developing the package's meta-analysis vignette. DJW was supported by NIH Grant
R01-GM101352. FM was supported by iDigBio, and therefore this material is based
upon work supported by the National Science Foundation’s Advancing Digitization
of Biodiversity Collections Program (Cooperative Agreement EF-1115210).
